\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Amrit Sinha} \\ \vspace{1pt}
    \small +919958508011 $|$ \href{mailto:amrit-sinha@outlook.com}{\underline{amrit-sinha@outlook.com}} $|$
    \href{https://linkedin.com/in/amritksinha}{\underline{LinkedIn}} $|$
    \href{https://github.com/amrit-sinha}{\underline{Github}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {BITS Pilani}{}
      {B.E. (Hons.) Electronics and Instrumentation}{2020 -- 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart


\resumeSubheading
  {Instahyre}{March 2025 -- June 2026}
  {SDE 1}{}
  \resumeItemListStart
    \resumeItem{\textbf{Tech Stack: Python, Django, MySQL, Redis, RabbitMQ, Elasticsearch, React, Jinja, HTML, CSS}}
    \resumeItem{Built a \textbf{TypeScript MCP stdio server} integrating AI reviewers with Phabricator, automating review-context generation from Differential diffs, changed files, and linked tasks.}
    \resumeItem{Integrated \textbf{AI coding assistants (Claude Code, GPT-Codex)} into the development workflow to automate boilerplate generation and feature scaffolding, enabling faster iteration and improved developer productivity.}
    \resumeItem{Implemented a \textbf{Redis-based sliding window rate limiter} using Lua scripts for atomic execution, throttling outbound emails to comply with AWS SES limits.}
    \resumeItem{Optimized \textbf{high-traffic API endpoints} with \textbf{p99 latencies exceeding 1000ms}, reducing them to under \textbf{300ms}.}
    \resumeItem{Designed and implemented a \textbf{Redis-backed OTP verification flow}, preventing premature database updates and ensuring secure phone number and email changes.}
    \resumeItem{Led a \textbf{large-scale refactor} to modularize the candidate-side application, reducing code coupling and accelerating feature development.}
    \resumeItem{Built and upgraded \textbf{UI components} using Jinja Templates, HTML, and custom CSS, improving responsiveness and maintainability.}
  \resumeItemListEnd

\resumeSubheading
  {ofScale}{Nov 2024 -- Jan 2025}
  {Full Stack Engineer Intern}{}
  \resumeItemListStart
    \resumeItem{\textbf{Tech Stack: JavaScript, React.js, Next.js, Tailwind CSS, Golang, MySQL}}
    \resumeItem{Developed and implemented the \textbf{mobile view} for the entire admin management website.}
    \resumeItem{Developed a \textbf{cron scheduler in Go} utilizing the gocron library, from initial design to final implementation.}
  \resumeItemListEnd

\resumeSubheading
  {Zluri Technologies}{Jul 2023 -- Dec 2023}
  {Full Stack Engineer Intern}{}
  \resumeItemListStart
    \resumeItem{\textbf{Tech Stack: JavaScript, Node.js, React.js, Next.js, Express.js, MongoDB, PostgreSQL}}
    \resumeItem{Built a \textbf{currency conversion feature} leveraging the Exchange Rate API to provide real-time and historical exchange rates.}
    \resumeItem{Migrated APIs to a new database architecture, reducing \textbf{response times by nearly 40\%}.}
  \resumeItemListEnd


\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\href{https://github.com/amrit-sinha/multimodal-rag}{\textbf{\underline{Multimodal RAG Backend}}} $|$ \textbf{Python, FastAPI, Celery, Redis, PostgreSQL, Docker}}{2026}
          \resumeItemListStart
            \resumeItem{Built a \textbf{document Q\&A backend} (FastAPI) for PDF/image uploads with RAG and page-level citations.}
            \resumeItem{Designed an \textbf{async ingestion flow} with presigned \textbf{MinIO} uploads and a \textbf{background Celery worker} that indexes files with pollable ingestion job status and retries.}
           \resumeItem{Implemented \textbf{text and image retrieval} over Postgres + pgvector using \textbf{BGE} for passages and \textbf{CLIP} for images, feeding matched sources to \textbf{Gemma4 (12b)} via \textbf{Ollama} for grounded, cited answers.}
            \resumeItem{Added \textbf{SSE streaming}, optional API-key auth, Redis rate limiting, and Docker Compose deployment.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Concepts}{: Data Structures, Algorithms, Object-Oriented Programming, Operating Systems, Computer Networks, System Design (HLD, LLD)} \\
     \textbf{Languages}{: JavaScript, TypeScript, Golang, Java, Python, C, C++, HTML5, CSS3, SQL} \\
     \textbf{Frameworks \& Libraries}{: React.js, Next.js, Redux, Angular, Node.js, Express.js, Bun.js, Django, Django Rest Framework, FastAPI, Celery, Tailwind CSS, Bootstrap, Jinja} \\
     \textbf{Databases, \& Messaging}{: PostgreSQL, MySQL, MongoDB, Elasticsearch, pgvector, Redis, RabbitMQ, Kafka} \\
     \textbf{Tools \& AI}{: Git, Linux, Docker, Kubernetes, AWS, Figma, Mercurial, Claude Code, GPT-Codex, RAG, MCP}
    }}
 \end{itemize}


%

%-------------------------------------------
\end{document}
